---
title: "flod"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flod}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(flod)
library(flowCore)
```

## Getting data into your working environment
Read in the .fcs files using `flowCore::read.flowSet()`. 
The flowSet is an S4 class and a convenient way of storing related .fcs files in a single object. 
However, being an S4 object, it is naturally restricted in its
scope to the registered methods and, thus, foregoes potentially relevant
functions for EDA, transformation, and modelling from other packages.

```{r}
data(GvHD, package = "flowCore")
GvHD
```

Turn it into a `tibble` using `flod::to_tibble()`

```{r}
flod::to_tibble(GvHD)
```

The function defaults to all slots of the flowSet, or accepts a user specified selection:

```{r}
to_tibble(GvHD, c("exprs", "keywords"))
```

See `?to_tibble` for a list of accepted keywords.