---
title: "Overview: synthetic data"
vignette: >
  %\VignetteIndexEntry{Synthetic flow cytometry data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

flod ships with a small synthetic dataset inside of a DuckDB database: 

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(duckdb)
library(flod)

con <- DBI::dbConnect(duckdb::duckdb(), system.file("extdata", "synthetic_data.duckdb", package = "flod"))
tables <- DBI::dbListTables(con)
tables
```

It was designed for exposition of data visualization and modelling by providing a realistic set of experiments, including failed runs and dead samples.

```{r}
sample1 <- DBI::dbGetQuery(con, "
  SELECT unnest(exprs, recursive := true) FROM experiment1 WHERE rowid = 0
")
head(sample1)
```

Every event also carries ground-truth labels for the gates it belongs to, which makes it well suited for teaching supervised approaches to gating and quality control.

## Data visualization
We'll start exploring the data to expose gating hierarchy and summary statistics:

```{r}
ggplot(sample1, aes(x = `FSC-A`, y = `FL1-A`)) +
  geom_hex() +
  theme_minimal() +
  scale_y_continuous(transform = "asinh")
```

